---
title: "Analysis"
author: "Tina Lasisi"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  pdf_document: default
  workflowr::wflow_html:
    toc: yes
    number_sections: yes
editor_options:
  chunk_output_type: console
header-includes: \usepackage{booktabs}

---


```{r setup, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(tidyverse)
library(knitr)
library(fs)
library(gridExtra)
library(patchwork)
library(broom.mixed)
library(huxtable)
library(jtools)
library(ggstance)
library(ggstatsplot)
library(PMCMRplus)
library(kableExtra)
# knitting to pdf
# rmarkdown::render(input = "analysis/analysis.Rmd", output_format = "pdf_document", output_dir = "output")
F = rprojroot::is_rstudio_project$make_fix_file()
palettedf <- tibble(paletteer::palettes_d_names)
# filter(.data = palettedf, length > 10 & type == "qualitative")
knitr::opts_chunk$set(echo = FALSE, include = TRUE, eval = TRUE, warning = FALSE, message = FALSE, fig.retina = 2, fig.width = 10, fig.height = 5, out.width = "95%", tidy.opts = list(width.cutoff = 55), tidy = TRUE)

knitr::opts_knit$set(root.dir = "..")
```


```{r functions, include=FALSE}
# This is a function to save the figures
plot_path = F("output/")
plot_path2 = F("output/manuscript_figures")
pltsave_func <- function(plot, plot_path, width, height){
  ggsave(
      filename = paste0(deparse(substitute(plot)), ".png"),
      plot = plot, 
      path = plot_path,
      width = width,
      height = height)
}

every_nth <- function(x, nth, empty = TRUE, inverse = FALSE) 
  {
  if (!inverse) {
    if(empty) {
      x[1:nth == 1] <- ""
      x
      } else {
        x[1:nth != 1]
        }
    } else {
      if(empty) {
        x[1:nth != 1] <- ""
        x
        } else {
          x[1:nth == 1]
        }
    }
}
```

```{r plothelpers, include=FALSE}

# Plot data as as a row of bar charts, each column being a different wind speed.
dryHairColor1 = "#E69F00"
wetHairColor1 = "#0072B2"
dryHairColor2 = "#E69F00"
wetHairColor2 = "#0072B2"
dryHairColor3 = "#E69F00"
wetHairColor3 = "#0072B2"

dryHairColor = dryHairColor1
wetHairColor = wetHairColor1

radiationOnHairColor = "red"
radiationOffHairColor = "blue"


coloursList <- c(dryHairColor1, dryHairColor2, dryHairColor3, wetHairColor1, wetHairColor2)
# Name your list of colors
names(coloursList) <- c('dry_1', 'dry_2', 'dry_3', 'wet_1', 'wet_2')

coloursList2 <- c(radiationOnHairColor, radiationOnHairColor, radiationOnHairColor, radiationOffHairColor, radiationOffHairColor, radiationOffHairColor)
names(coloursList2) <- c('on_1', 'on_2', 'on_3', 'off_1', 'off_2', 'off_3')


radiation_names <- c(
  `on` = 'Radiation On',
  `off` = 'Radiation Off'
)


wind_names <- c(
  `0.3` = paste0(0.3,"~~","frac(m , s)"),
  `1` = paste0('1' ,"~~","frac(m , s)"),
  `2.5` = paste0(2.5,"~~","frac(m , s)")
)



# df_sweat_requirements['sweat_zero'][df_sweat_requirements['sweat_zero'] < 0] <- 0

```

# Preparing Data

First, we import the data and label the variables.

```{r Importing, echo=FALSE}
# Importing data

df_wetdry <- read_csv(F("data/current/Aug2022.csv"), 
    col_types = cols(
      wig = col_factor(levels = c("nude", 
        "Low_curve", "Mid_curve", "High_curve")), 
      radiation = col_factor(levels = c("off", 
            "on")),
      wet_dry = col_factor(levels = c("dry", 
            "wet")),
      trial = col_factor(levels = c("1", "2", "3")))) %>% 
  mutate(wig = factor(wig, levels = c("nude", 
        "Low_curve", "Mid_curve", "High_curve"), labels = c("Nude", 
        "Straight", "Moderately\nCurled", "Tightly\nCurled"))) %>% 
  rename(heat_loss = heatloss) %>% drop_na

df_wetdry_plots <- df_wetdry %>% 
  unite('data_points', c('radiation','trial'), remove=FALSE)

```

### Data preview

```{r Data-preview, echo=TRUE}
# Preview data
head(df_wetdry) %>% 
  kbl(booktabs=T) %>% 
  kable_styling(latex_options=c("striped", "scale_down"))

```


### Plots
```{r General-Plots, echo=FALSE}

raw_barplot <- ggplot(df_wetdry_plots, aes(x = wig, y = heat_loss, fill = data_points)) + 
  geom_bar(stat = "identity", position = "dodge", colour="black") + 
  facet_grid(wet_dry ~ wind, labeller = labeller(radiation = as_labeller(radiation_names),
                                                   wind = as_labeller(wind_names, label_parsed)))+ 
  scale_fill_manual(values = coloursList2, breaks = c('on_1', 'off_1'), labels = c('Radiation On', 'Radiation Off')) + 
  labs(x = "", y = expression(paste("Heat Loss ( ", frac("W","m"^"2"), ' )')), fill = '') + 
scale_color_discrete(guide = "none") +  theme_classic()

raw_barplot

```




```{r General-Not-Used}

change_winds <- function(df, windCol, wigCol) {
  df[windCol] <- df[windCol] + (0.1)*(ifelse(df[wigCol] == "Nude", 0, ifelse(df[wigCol] == "Straight", -0.5, ifelse(df[wigCol] == "Moderately\nCurled", 0, 0.5))))
  return(df)
}

df_wetdry_plots <- change_winds(df_wetdry_plots, 'wind', 'wig')
# view(df_wetdry_plots['wind'])

# 
# # SCATTER PLOT
# raw_scatter <- ggplot(df_wetdry_plots, aes(x = wind, y = heat_loss, shape = wig, fill = wet_dry)) +
#   geom_point(size = 2) +
#   facet_grid(. ~ radiation, labeller = labeller(radiation = as_labeller(radiation_names))) +
#   scale_fill_manual(values = c(dryHairColor, wetHairColor)) +
#   scale_shape_manual(values = c(21,22,25,24)) + 
# 
#   scale_y_continuous(breaks= seq(0,500,25),
#     labels = every_nth(seq(0,500,25), 3, inverse = TRUE)) +
# 
#   scale_x_continuous(limits = c(0, 3), breaks = c(0, 0.5, 1, 1.5, 2, 2.5)) +
#   guides(fill = guide_legend(override.aes=list(shape=21))) +
#   labs(x = expression(paste("Wind Speed ( ", frac("m", "s"), ' )')), y = expression(paste("Heat Loss ( ", frac("W","m"^"2"), ' )'))) +
# theme_classic() + theme( panel.grid.major = element_blank(),
# panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
# 
# raw_scatter
``` 

## Removing Outlier
It was noticed that the 2nd trial conducted with wet, tightly curled hair, 2.5 m/s wind speed, and radiation on, had more heat loss than any of the trials with radiation off. With the understanding that radiation should always decrease heat loss, we elected to remove that data point.

```{r Outlier, echo=TRUE}
# Remove specific entry
df_wetdry <- df_wetdry %>% filter(!(wig == "Tightly\nCurled" & wind == 2.5 & radiation == "on" & wet_dry == "wet" & trial == "1"))

```


```{r General-After-Outlier-Removal}
df_wetdry_plots <- df_wetdry %>% 
  unite('data_points', c('radiation','trial'), remove=FALSE)

raw_barplot_minoutlier <- ggplot(df_wetdry_plots, aes(x = wig, y = heat_loss, fill = data_points)) + 
  geom_bar(stat = "identity", position = "dodge", colour="black") + 
  facet_grid(wet_dry ~ wind, labeller = labeller(radiation = as_labeller(radiation_names),
                                                   wind = as_labeller(wind_names, label_parsed)))+ 
  scale_fill_manual(values = coloursList2, breaks = c('on_1', 'off_1'), labels = c('Radiation On', 'Radiation Off')) + 
  labs(x = "", y = expression(paste("Heat Loss ( ", frac("W","m"^"2"), ' )')), fill = '') + 
scale_color_discrete(guide = "none") + theme_classic() + scale_y_continuous(breaks=seq(0,450,150))

raw_barplot_minoutlier

manuscript_plt1 <- raw_barplot_minoutlier + coord_flip()
```


# Regression models

```{r df-solar-influx}

df_influx <- df_wetdry %>% 
  pivot_longer(cols = c("heat_loss", "resistance", "clo")) %>% 
  filter(name == "heat_loss") %>% 
  select(-c(skin_temp, amb_temp, amb_rh)) %>% 
  pivot_wider(names_from = radiation, values_from = value) %>% 
  mutate(influx = off-on) %>% 
  drop_na() %>% 
  select(-name)

```

```{r df-30c-radoff, include=FALSE}

df_dry_off <- df_wetdry %>% 
  filter(radiation=="off" & wet_dry == "dry") %>% 
  select(c(wig, wind, wet_dry, resistance, trial)) %>% 
  distinct()

df_dry_off

df_dry30_off<- df_influx %>% 
  filter(wet_dry == "dry") %>% 
  left_join(., 
            df_dry_off) %>% 
  mutate(heatloss30 = 5/resistance) %>% 
  select(-c(on, off)) %>% 
  rename(off = heatloss30) %>% 
  distinct()

df_dry30_off

```

```{r df-30c-radon, include=FALSE}

df_dry_on <- df_wetdry %>% 
  filter(radiation=="on" & wet_dry =="dry") %>% 
  select(c(wig, wind, wet_dry, resistance, trial)) %>% 
  distinct()

df_dry_on

df_dry30<- df_dry30_off %>% 
  mutate(on = off-influx) %>% 
  select(-resistance) %>% 
  distinct()

df_dry30
```

```{r df-wet-dry, include=FALSE}

df_wetdry_final <- bind_rows(df_dry30, df_influx[df_influx$wet_dry == "wet",]) %>% 
  distinct()

df_wetdry_final

df_long_wetdry_final <- df_wetdry_final %>% 
  pivot_longer(influx:on, names_to = "var", values_to = "heatloss") %>% 
  distinct()

df_long_wetdry_final

```


### Radiation off

Here, we model the effect of the `wig` variable on the `off` (heat loss without radiation) variable while correcting for `wind`. 

Without radiation, having hair will reduce the heat loss.

```{r lm-dry-heatloss-off}

# df <- df_wetdry_final %>% 
#   filter(wet_dry == "dry")

df_dry_off <- df_wetdry_final %>%
  filter(wet_dry == "dry")

# df_dry_off
model_dry_off<- lm(off~wind+wig, data=df_dry_off)
summary(model_dry_off)

```


### Radiation on

With radiation, there is a net increase in heat (i.e. heat gain) without any hair. Additonally, we observe that heat gain decreases with increasingly curled hair.

```{r lm-dry-heatloss-on}
# 
# df <- df_wetdry_final %>% 
#   filter(wet_dry == "dry")
df_dry_on <- df_wetdry_final %>% 
  filter(wet_dry == "dry")

model_dry_on<- lm(on~wind+wig, data=df_dry_on)
summary(model_dry_on)



# summ(model_dry_on, scale = TRUE, confint = TRUE, digits = 5)
# 
# plot_summs(model_dry_on, scale = TRUE, inner_ci_level = .9)
```

### Solar influx

Here, we model the effect of the `wig` variable on `influx` while correcting for `wind`. 

In the dry heat loss experiments, we see that all hair (regardless of curliness) decreases the solar influx. Additionally, the curlier the hair, the lower the solar influx.


```{r lm-dry-influx}
df_dry <- df_wetdry_final %>% 
  filter(wet_dry == "dry")


model_dry_influx <- lm(influx~wind+wig, data=df_dry)

summary(model_dry_influx)
```


### Summary of dry heat loss regression models


```{r lm-summary, echo=FALSE, results='asis'}
# export_summs(model_dry_off, model_dry_on, model_dry, scale = TRUE, error_format = "[{conf.low}, {conf.high}]", model.names = c("Radiation Off", "Radiation On", "Solar Influx"))
export_summs(model_dry_off, model_dry_on, model_dry_influx, error_format = "[{conf.low}, {conf.high}]", model.names = c("Radiation Off", "Radiation On", "Solar Influx"))
```


```{r lm-save-dry, eval=FALSE, include=FALSE}
manuscript_tbl_dry_lm <- export_summs(model_dry_off, model_dry_on, model_dry_influx, error_format = "[{conf.low}, {conf.high}]", model.names = c("Radiation Off", "Radiation On", "Solar Influx"), to.file = "docx", file.name = "output/manuscript_tbl_dry_lm.docx")

```

```{r plt-summary-models, echo=FALSE, fig.cap="Regression coefficients across regression models.", fig.height=3, fig.width=5, out.width="60%", fig.align='center'}

# scaled 
# plot_summs(model_dry_off, model_dry_on, model_dry_influx, scale = TRUE,  model.names = c("Radiation Off", "Radiation On", "Solar Influx"))

# unscaled 
manuscript_plt_dry_lm <- plot_summs(model_dry_off, model_dry_on, model_dry_influx,  model.names = c("Radiation Off", "Radiation On", "Solar Influx"))

manuscript_plt_dry_lm

```


### Dry heat loss ANOVA plots
```{r ggbetweenstats-dry, fig.align='center', fig.width=10, fig.height=6, fig.cap="ANOVA of dry heat loss"}

data_long <- df_dry %>%
  pivot_longer(cols = c("influx", "off", "on"), names_to = "variable", values_to = "value") %>% 
  mutate(variable = factor(variable, 
                           levels = c("off", "on", "influx"),
                           labels = c("Radiation Off", "Radiation On", "Solar Influx")))


# Create the plot using grouped_ggbetweenstats
ggstatsplot::grouped_ggbetweenstats(
  data = data_long,
  x = wig,
  y = value,
  xlab = "Wig",
  ylab = "Heat influx",
  grouping.var = variable,
  type = "np", # non-parametric
  pairwise.comparisons = TRUE,
  pairwise.display = "s",
  p.adjust.method = "bonferroni",
  results.subtitle = FALSE,
  ggtheme = ggplot2::theme_bw(),
  ggplot.component = list(theme(plot.subtitle = element_text(size = 6), axis.title.y.right = element_text(size = 6))))
```


## Evaporative resistance (wet experiments)

Here, we repeat the same modelling process for the evaporative resistance data from the wet experiments.


### Radiation off

Here, we model the effect of the `wig` variable on the `off` (heat loss without radiation) variable while correcting for `wind`. 

Without solar radiation, all hair (regardless of texture) decreases evaporative resistance. 

```{r lm-wet-heatloss-off}

df <- df_wetdry_final %>% 
  filter(wet_dry == "wet")
df_wet_off <- df_wetdry_final %>% 
  filter(wet_dry == "wet")
model_wet_off<- lm(off~wind+wig, data=df_wet_off)
summary(model_wet_off)
```

### Radiation on

With radiation, hair decreases evaporative resistance. 

```{r lm-wet-heatloss-on}

df <- df_wetdry_final %>% 
  filter(wet_dry == "wet")
df_wet_on <- df_wetdry_final %>% 
  filter(wet_dry == "wet")
model_wet_on<- lm(on~wind+wig, data=df_wet_on)
summary(model_wet_on)
```


### Solar influx

Combining the above data to calculate solar influx, we see that there is not a considerable effect of radiation on evaporative resistance.

```{r lm-wet-influx}

df <- df_wetdry_final %>% 
  filter(wet_dry == "wet")

df_wet <- df_wetdry_final %>% 
  filter(wet_dry == "wet")

model_wet <- lm(influx~wind+wig, data=df_wet)

# model_wet

# plot(model_wet)
summary(model_wet)
```

### Summary of evaporative heat loss regression models


```{r lm-summary-wet, echo=FALSE, results='asis'}

# export_summs(model_wet_off, model_weet_on, model_wet, scale = TRUE, error_format = "[{conf.low}, {conf.high}]", model.names = c("Radiation Off", "Radiation On", "Solar Influx"))
export_summs(model_wet_off, model_wet_on, model_wet, error_format = "[{conf.low}, {conf.high}]", model.names = c("Radiation Off", "Radiation On", "Solar Influx"))

```

```{r lm-save-wet, eval=FALSE, include=FALSE}
manuscript_tbl_wet_lm <- export_summs(model_wet_off, model_wet_on, model_wet, error_format = "[{conf.low}, {conf.high}]", model.names = c("Radiation Off", "Radiation On", "Solar Influx"), to.file = "docx", file.name = "output/manuscript_tbl_wet_lm.docx")
```

```{r plt-summary-models-wet, echo=FALSE, fig.cap="Regression coefficients across regression models.", fig.height=3, fig.width=5, out.width="60%", fig.align='center'}

# scaled 
# plot_summs(model_wet_off, model_wet_on, model_wet, scale = TRUE,  model.names = c("Radiation Off", "Radiation On", "Solar Influx"))

# unscaled 

manuscript_plt_wet_lm <- plot_summs(model_wet_off, model_wet_on, model_wet,  model.names = c("Radiation Off", "Radiation On", "Solar Influx"))

manuscript_plt_wet_lm

```

### Evaporative heat ANOVA plots

```{r ggbetweenstats-wet, fig.align='center', fig.width=10, fig.height=6, fig.cap="ANOVA of evaporative heat loss"}

data_long <- df_wet %>%
  pivot_longer(cols = c("influx", "off", "on"), names_to = "variable", values_to = "value") %>% 
  mutate(variable = factor(variable, 
                           levels = c("off", "on", "influx"),
                           labels = c("Radiation Off", "Radiation On", "Solar Influx")))


# Create the plot using grouped_ggbetweenstats
ggstatsplot::grouped_ggbetweenstats(
  data = data_long,
  x = wig,
  y = value,
  xlab = "Wig",
  ylab = "Heat influx",
  grouping.var = variable,
  type = "np", # non-parametric
  pairwise.comparisons = TRUE,
  pairwise.display = "s",
  p.adjust.method = "bonferroni",
  results.subtitle = FALSE,
  ggtheme = ggplot2::theme_bw(),
  ggplot.component = list(theme(plot.subtitle = element_text(size = 6), axis.title.y.right = element_text(size = 6))))
```



# Calculating Thermal Resistance

$$I_t = \frac{T_{Skin} - T_{Air}}{H_{Dry}}$$

```{r Thermal-Resistance, echo=TRUE}

df_wetdry['dry_heat_resistance'] <- (df_wetdry['skin_temp'] - df_wetdry['amb_temp']) / df_wetdry['heat_loss']

# For the dry data, leave this blank
df_wetdry <- df_wetdry %>% mutate(dry_heat_resistance = ifelse(wet_dry == 'wet', NaN, dry_heat_resistance))

```

```{r Thermal-Resistance-Plots, echo=FALSE}
# Plot dry

dry_resist <- ggplot(df_wetdry, aes(x = wig, y = dry_heat_resistance, fill = trial)) + 
  geom_bar(stat = "identity", position = "dodge", colour = "black") + 
  facet_grid(radiation ~ wind, labeller = labeller(radiation = as_labeller(radiation_names),
                                                   wind = as_labeller(wind_names, label_parsed)))+ 
  scale_fill_manual(values = c(dryHairColor1, dryHairColor2, dryHairColor3), breaks = NULL, labels = c()) + 
  labs(x = '', y = expression(paste("Dry Heat Resistance ( ", frac("m"^"2"*"K","W"), ' )')), fill = '') + 
scale_color_discrete(guide = "none") +  theme_classic()

dry_resist

manuscript_plt5 <- dry_resist


df_wetdry_plots2 <- df_wetdry
df_wetdry_plots2 <- change_winds(df_wetdry_plots2, 'wind', 'wig')
```

```{r ThermalResistance-plt2, echo=FALSE, include=FALSE}
# Scatter plot dry

# ggplot(df_wetdry_plots2, aes(x = wind, y = dry_heat_resistance, shape = wig, fill = radiation)) +
#   geom_point(size = 2) +
#   scale_fill_manual(values = c('green', 'red')) +
#   scale_shape_manual(values = c(21,22,23,24)) + 
#   scale_y_continuous(breaks= seq(0,2,0.25),
#     labels = every_nth(seq(0,2,0.25), 2, inverse = TRUE)) +
#   scale_x_continuous(limits = c(0,2.7), breaks = c(0, 0.5, 1, 1.5, 2, 2.5)) +
#   guides(fill = guide_legend(override.aes=list(shape=21))) +
#   labs(x = expression(paste("Wind Speed ( ", frac("m", "s"), ' )')), y = expression(paste("Dry Heat Resistance ( ",  frac("m"^"2"*"K","W"), ' )'))) +
# theme_classic() + theme( panel.grid.major = element_blank(),
# panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))

```

# Calculating Net Solar Influx

$$I_{Dry} = H_{Dry} - H_{Dry}^{Solar}$$ $$I_{Evap} = H_{Evap} - H_{Evap}^{Solar}$$

```{r net-solar-influx, echo=TRUE}

# Average all trials with the same characteristics
df_averaged_trials <- df_wetdry %>%
  group_by(wig, wind, radiation, wet_dry) %>%
  drop_na(heat_loss) %>%
  summarise(heat_loss = mean(heat_loss))

# Pivot the dataframe to incldue radiation on and off as part of same event
df_radiation_split <- df_averaged_trials %>%
  pivot_wider(names_from = c(radiation), values_from = c(heat_loss)) %>% 
  rename(heat_loss_off = off) %>% 
  rename(heat_loss_on = on)

# Calculate the net influx
df_net_influx_plots <- df_radiation_split %>%
  group_by(wig, wind) %>%
  summarise(wet_dry = wet_dry,
            net_influx = heat_loss_off - heat_loss_on) 

df_net_influx <- df_net_influx_plots %>%  spread(wet_dry, net_influx)
```

```{r net-solar-influx-plts, echo=FALSE}
plt_influx_bar <- ggplot(df_net_influx_plots, aes(x = wig, y = net_influx, fill = wet_dry)) + 
  geom_bar(stat = "identity", position = "dodge", color = "black") + 
  facet_grid(. ~ wind, labeller = labeller(wind = as_labeller(wind_names, label_parsed)))+ 
  scale_fill_manual(values = c(dryHairColor, wetHairColor), labels = c("dry", "wet")) + 
  labs(x = "", y = expression(paste("Net Solar Influx ( ", frac("W","m"^"2"), ' )')), fill = '') + 
scale_color_discrete(guide = "none") +  theme_classic()

plt_influx_bar

plt_influx_pointline <- ggplot(df_net_influx_plots, aes(x = wind, y = net_influx, shape = wig, fill = wig)) +
  geom_point(size = 3) +
  geom_line() +
  facet_grid(. ~ wet_dry, labeller = as_labeller(c(`dry` = 'A. Dry', `wet` = 'B. Wet')))+ 
  scale_fill_manual(values = c("red","blue","pink","orange")) +
  scale_shape_manual(values = c(21,22,23,24)) + 
  scale_y_continuous(breaks= seq(0,180,25),
    labels = every_nth(seq(0,180,25), 2, inverse = TRUE)) +
  scale_x_continuous(limits = c(0,2.7), breaks = c(0, 0.5, 1, 1.5, 2, 2.5)) +
  # guides(fill = guide_legend(override.aes=list(shape=21))) +
  labs(x = expression(paste("Wind Speed ( ", frac("m", "s"), ' )')), y = expression(paste("Net Solar Influx ( ", frac("W","m"^"2"), ' )'))) +
theme_classic() + theme( panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))

plt_influx_pointline

manuscript_plt2 <- plt_influx_pointline
```

```{r plt-solar-influx-more, echo=FALSE, include=FALSE}
ggplot(df_net_influx_plots, aes(x = wind, y = net_influx, shape = wig, fill = wet_dry)) +
  geom_point(size = 3) +
  geom_line() +
  scale_fill_manual(values = c(dryHairColor, wetHairColor)) +
  scale_shape_manual(values = c(21,22,23,24)) +
  scale_y_continuous(breaks= seq(0,180,25),
    labels = every_nth(seq(0,180,25), 2, inverse = TRUE)) +
  scale_x_continuous(limits = c(0,2.7), breaks = c(0, 0.5, 1, 1.5, 2, 2.5)) +
  guides(fill = guide_legend(override.aes=list(shape=21))) +
  labs(x = expression(paste("Wind Speed ( ", frac("m", "s"), ' )')), y = expression(paste("Net Solar Influx ( ", frac("W","m"^"2"), ' )'))) +
theme_classic() + theme( panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
```

# Adjusting Heat Losses to 30 Degrees Celsius

## Dry Heat Loss

$$H_{Dry}^{30^\circ C} = \frac{35 -30}{I_t}$$

```{r heat-adj, echo=TRUE}

# Their calculation
df_wetdry['heat_30'] = (35 - 30) / df_wetdry['dry_heat_resistance']

# What I would expect
#df_wetdry['heat_30'] = (df_wetdry['skin_temp'] - 30) / df_wetdry['dry_heat_resistance']


# Recreate the radiation split dataframe to include heat_30
df_averaged_trials <- df_wetdry %>%
  group_by(wig, wind, radiation, wet_dry) %>%
  drop_na(heat_loss) %>%
  summarise(heat_loss = mean(heat_loss),
    heat_30 = mean(heat_30))

df_radiation_split <- df_averaged_trials %>%
  pivot_wider(names_from = c(radiation), values_from = c(heat_loss, heat_30))
```


## Dry and Wet Heat Losses With Solar Radiation

$$H_{Dry}^{30^{\circ} C,\:Solar} = H_{Dry}^{30^{\circ} C} - I_{Dry}$$ $$H_{Wet}^{30^{\circ} C,\:Solar} = H_{Evap + Dry}^{30^{\circ} C} = H_{Evap} + I_{Dry} + H_{Dry}^{30^{\circ} C,\:Solar}$$

```{r heatloss-radiation, echo=TRUE}

dry_heat_30 = df_radiation_split[df_radiation_split$wet_dry == 'dry',]

heat_evap = df_radiation_split[df_radiation_split$wet_dry == 'wet',]


df_adjusted_solar <- data.frame(
  dry_heat_loss <- dry_heat_30$heat_30_off - df_net_influx$dry,
  wind <- dry_heat_30$wind,
  wig <- dry_heat_30$wig
) %>% rename('dry_heat_loss' = 'dry_heat_loss....dry_heat_30.heat_30_off...df_net_influx.dry') %>%
  rename('wind' = 'wind....dry_heat_30.wind') %>%
  rename('wig' = 'wig....dry_heat_30.wig')


df_adjusted_solar['wet_heat_loss'] <-  + heat_evap$heat_loss_on + df_net_influx$dry + df_adjusted_solar$dry_heat_loss


df_adjusted_solar_plots <-df_adjusted_solar %>% 
  pivot_longer(cols = c('dry_heat_loss', 'wet_heat_loss'), names_to = 'wet_dry', values_to = 'heat_loss')
```

```{r plt-heatloss-radiation, echo=FALSE}

plt_30_solar_bar <- ggplot(df_adjusted_solar_plots, aes(x = wig, y = heat_loss, fill = wet_dry)) + 
  geom_bar(stat = "identity", position = "dodge", color = "black") + 
  facet_grid(wind ~ ., labeller = labeller(wind = as_labeller(wind_names, label_parsed)))+
  # facet_grid(. ~ wind, labeller = labeller(wind = as_labeller(wind_names, label_parsed)))+
  scale_fill_manual(values = c(dryHairColor, wetHairColor), labels = c("dry", "wet")) + 
  labs(title = 'Heat Loss with Solar Radiation at 30C', x = "", y = expression(paste("Heat Loss ( ", frac("W","m"^"2"), ' )')), fill = '') + 
scale_color_discrete(guide = "none") +  theme_classic() + coord_flip()

plt_30_solar_bar

v2_manuscript_plt1 <- ggplot(df_adjusted_solar_plots, aes(x = wig, y = heat_loss, fill = wet_dry)) + 
  geom_bar(stat = "identity", position = "dodge", color = "black") + 
  facet_grid(wind ~ ., labeller = labeller(wind = as_labeller(wind_names, label_parsed)))+
  # facet_grid(. ~ wind, labeller = labeller(wind = as_labeller(wind_names, label_parsed)))+
  scale_fill_manual(values = c(dryHairColor, wetHairColor), labels = c("dry", "wet")) + 
  labs(x = "", y = expression(paste("Heat Loss ( ", frac("W","m"^"2"), ' )')), fill = '') + 
scale_color_discrete(guide = "none") +  theme_classic() + coord_flip()

# df_adjusted_solar30_plts_dry <- df_adjusted_solar_plots %>% filter(wet_dry == "dry_heat_loss")

# ggplot(df_adjusted_solar30_plts_dry, aes(x = wig, y = heat_loss, fill = wet_dry)) + 
#   geom_bar(stat = "identity", position = "dodge", color = "black") + 
#   facet_grid(wind ~ ., labeller = labeller(wind = as_labeller(wind_names, label_parsed)))+
#   # facet_grid(. ~ wind, labeller = labeller(wind = as_labeller(wind_names, label_parsed)))+ 
#   scale_fill_manual(values = c(dryHairColor, wetHairColor), labels = c("dry", "wet")) + 
#   labs(title = 'Heat Loss with Solar Radiation at 30C', x = "", y = expression(paste("Heat Loss ( ", frac("W","m"^"2"), ' )')), fill = '') + 
# scale_color_discrete(guide = "none") +  theme_classic() 

plt_30_solar_pointline <- ggplot(df_adjusted_solar_plots, aes(x = wind, y = heat_loss, shape = wig, fill = wet_dry)) +
  geom_point(size = 3) +
  geom_line() +
  scale_fill_manual(values = c(dryHairColor, wetHairColor), labels = c("dry", "wet")) +
  scale_shape_manual(values = c(21,22,23,24)) + 
  scale_y_continuous(breaks= seq(-300,400,25),
    labels = every_nth(seq(-300,400,25), 4, inverse = TRUE)) +
  scale_x_continuous(limits = c(0,2.7), breaks = c(0, 0.5, 1, 1.5, 2, 2.5)) +
  guides(fill = guide_legend(override.aes=list(shape=21))) +
  labs(title = 'Heat Loss with Solar Radiation at 30C', x = expression(paste("Wind Speed ( ", frac("m", "s"), ' )')), y = expression(paste("Heat Loss ( ", frac("W","m"^"2"), ' )'))) +
theme_classic() + theme( panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))

plt_30_solar_pointline
```

```{r plt-heatloss-radiation2, echo=FALSE, include=FALSE, fig.cap="Heat loss with solar radiation at 30C"}

plt_30_solar_pointline_panel <- ggplot(df_adjusted_solar_plots, aes(x = wind, y = heat_loss, shape = wig, fill = wig)) +
  geom_point(size = 3) +
  geom_line() +
  facet_grid(.~ wet_dry , labeller = as_labeller(c(`dry_heat_loss` = 'dry', `wet_heat_loss` = 'wet')))+ 
  scale_shape_manual(values = c(21,22,23,24)) + 
  scale_fill_manual(values=c("red","blue","pink","orange")) +
  scale_y_continuous(breaks= seq(-200,401,50),
    labels = every_nth(seq(-200,401,50), 2, inverse = TRUE)) +
  scale_x_continuous(limits = c(0,2.7), breaks = c(0, 0.5, 1, 1.5, 2, 2.5)) +
  # guides(fill = guide_legend(override.aes=list(shape=21))) +
  labs(x = expression(paste("Wind Speed ( ", frac("m", "s"), ' )')), y = expression(paste("Heat Loss ( ", frac("W","m"^"2"), ' )'))) +
theme_classic() + theme( panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))

plt_30_solar_pointline_panel 

manuscript_plt3 <- plt_30_solar_pointline_panel
```



# Calculating Evaporative Potential

$$H_{Max}^{30^{\circ} C,\:Solar} = H_{Wet}^{30^{\circ} C,\:Solar} - H_{Dry}^{30^{\circ} C,\:Solar}$$

```{r evap-potential, echo=TRUE}

df_evaporative_potential <- df_adjusted_solar$wet_heat_loss - df_adjusted_solar$dry_heat_loss

```

# Calculating Sweat Requirements

$$Sweat_{Max} = \frac{H_{Max}^{30^{\circ} C,\:Solar} * 3600}{2430}$$

$$ IF \; H_{Dry}^{30^{\circ} C,\:Solar} < 0, \; Sweat_{Zero} = -\frac{H_{Dry}^{30^{\circ} C,\:Solar} * 3600}{2430} \\
ELSE, \; Sweat_{Zero} = 0$$


```{r sweat-req, echo=TRUE}
# Create a new df with the sweat requirements

df_sweat_requirements <- data.frame(
  sweat_max <- df_evaporative_potential * 3600 / 2430,
  sweat_zero <- -3600 / 2430 * df_adjusted_solar['dry_heat_loss'],
  wig <- df_adjusted_solar$wig,
  wind <- df_adjusted_solar$wind
)

#Rename columns
colnames(df_sweat_requirements) <- c('sweat_max', 'sweat_zero', 'wig', 'wind')


#Replace all values less than 0 with 0 per formula
df_sweat_requirements['sweat_zero'][df_sweat_requirements['sweat_zero'] < 0] <- 0
```

```{r plt-sweat-req, echo=FALSE}

sweat_zero_plot <- ggplot(df_sweat_requirements, aes(x = wind, y = sweat_zero, shape = wig, fill = wig)) +
  geom_point(size = 3) +
  geom_line() +
  scale_shape_manual(values = c(21,22,23,24)) + 
  scale_fill_manual(values=c("red","blue","pink","orange")) +
  scale_y_continuous(breaks= seq(0,700,25),
    labels = every_nth(seq(0,700,25), 2, inverse = TRUE)) +
  scale_x_continuous(limits = c(0,2.7), breaks = c(0, 0.5, 1, 1.5, 2, 2.5)) +
# guides(fill = guide_legend(override.aes=list(shape=21))) +
  labs(x = expression(paste("Wind Speed ( ", frac("m", "s"), ' )')), y = expression(paste("Sweat ( ", frac("g","m"^"2"*"h"), ' )'))) +
theme_classic() + theme( panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))

sweat_max_plot <- ggplot(df_sweat_requirements, aes(x = wind, y = sweat_max, shape = wig, fill = wig)) +
  geom_point(size = 3) +
  geom_line() +
  scale_shape_manual(values = c(21,22,23,24)) + 
  scale_fill_manual(values=c("red","blue","pink","orange")) +
  scale_y_continuous(breaks= seq(0,700,25),
    labels = every_nth(seq(0,700,25), 4, inverse = TRUE)) +
  scale_x_continuous(limits = c(0,2.7), breaks = c(0, 0.5, 1, 1.5, 2, 2.5)) +
  labs(x = expression(paste("Wind Speed ( ", frac("m", "s"), ' )')), y = expression(paste("Sweat ( ", frac("g","m"^"2"*"h"), ' )'))) +
theme_classic() + theme( panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))


sweat_max_plot + sweat_zero_plot + plot_layout(guides = "collect") + plot_annotation(tag_levels = "A")

v2_manuscript_plt2 <- sweat_max_plot + sweat_zero_plot + plot_layout(guides = "collect") + plot_annotation(tag_levels = "A")

```


```{r plt sweat}

df_sweat_requirements_long <- df_sweat_requirements %>% 
  pivot_longer(cols = c('sweat_max', 'sweat_zero'), names_to = 'sweat', values_to = 'value')

sweat_combo_plot <- ggplot(df_sweat_requirements_long, aes(x = wind, y = value, shape = wig, fill = wig)) +
  geom_point(size = 3) +
  geom_line() +
  facet_grid(.~ sweat , labeller = as_labeller(c(`sweat_max` = 'A. Max evaporative cooling', `sweat_zero` = 'B. Zero heat gain')))+   scale_shape_manual(values = c(21,22,23,24)) + 
  scale_fill_manual(values=c("red","blue","pink","orange")) +
  scale_y_continuous(breaks= seq(0,700,50),
    labels = every_nth(seq(0,700,50), 2, inverse = TRUE)) +
  scale_x_continuous(limits = c(0,2.7), breaks = c(0, 0.5, 1, 1.5, 2, 2.5)) +
# guides(fill = guide_legend(override.aes=list(shape=21))) +
  labs(x = expression(paste("Wind Speed ( ", frac("m", "s"), ' )')), y = expression(paste("Sweat ( ", frac("g","m"^"2"*"h"), ' )'))) +
theme_classic() + theme( panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))

manuscript_plt4 <- sweat_combo_plot


```



```{r plt-combo-paper, eval=FALSE, include=FALSE}


manuscript_plt6 <- (manuscript_plt_dry_lm)+ (manuscript_plt_wet_lm + theme(axis.text.y = element_blank())) + plot_annotation(tag_levels = "A") + plot_layout(guides = "collect") & theme(legend.title = element_blank(), axis.title.x = element_blank(), legend.position = "bottom") 


manuscript_plt6

pltsave_func(manuscript_plt6, plot_path, width = 8, height = 4)

fig2 <- manuscript_plt6

pltsave_func(fig2, plot_path2, width = 8, height = 4)

# manuscript_plt1 + manuscript_plt5 + manuscript_plt6 + guide_area() + manuscript_plt2 + manuscript_plt3 + manuscript_plt4 + plot_layout(design = design, guides = "collect") + plot_annotation(tag_levels = "A")

left_plts <- manuscript_plt1 / manuscript_plt6 + plot_layout(guides = "auto", heights = c(1.5,1)) & theme(legend.position = 'bottom')

right_plts <- (manuscript_plt2 / manuscript_plt3 / manuscript_plt4 + plot_layout(guides = "collect"))

  patchwork <- left_plts | right_plts + plot_layout(widths = c(1.5, 1), guides = "collect")
  
  # left_plts | manuscript_plt2/ guide_area() | manuscript_plt3/ manuscript_plt4/ manuscript_plt5 + plot_layout(guides = "collect")
  
patchwork
  
  # patchwork <- manuscript_plt1 / manuscript_plt6 | (manuscript_plt2 / manuscript_plt3 / manuscript_plt4 + plot_layout(guides = "collect"))
  
  
manuscript_combo_fig <- patchwork + plot_annotation(tag_levels = "A")
 

manuscript_combo_fig

pltsave_func(manuscript_combo_fig, plot_path, width = 9, height = 8)


```

```{r plt-combo-paper-v2, include=FALSE}

# v2_manuscript_plt1

# pltsave_func(v2_manuscript_plt1, plot_path, width = 7, height = 5)

# pltsave_func(v2_manuscript_plt2, plot_path, width = 7, height = 4)
pltsave_func(sweat_combo_plot, plot_path, width = 7, height = 4)

v2_manuscriplt_plt_influx <- plt_influx_pointline

pltsave_func(v2_manuscriplt_plt_influx, plot_path, width = 7, height = 4)


```



