---
title: "Analysis"
author: "Tina Lasisi"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  workflowr::wflow_html:
    toc: yes
    number_sections: yes
editor_options:
  chunk_output_type: console
---

```{r setup, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(tidyverse)
library(knitr)
library(kableExtra)
library(fs)
library(ggstatsplot)
library(gridExtra)
library(patchwork)
library(jtools)
library(gtsummary)
# knitting to pdf
# rmarkdown::render(input = "analysis/analysis.Rmd", output_format = "pdf_document", output_dir = "output")
F = rprojroot::is_rstudio_project$make_fix_file()
palettedf <- tibble(paletteer::palettes_d_names)
# filter(.data = palettedf, length > 10 & type == "qualitative")
knitr::opts_chunk$set(echo = FALSE, include = TRUE, eval = TRUE, warning = FALSE, message = FALSE, fig.retina = 2, fig.width = 8, fig.height = 6, out.width = "100%")
```


```{r functions, include=FALSE}
# This is a function to save the figures
plot_path = F("output/")
pltsave_func <- function(plot, plot_path, width, height){
  ggsave(
      filename = paste0(deparse(substitute(plot)), ".png"),
      plot = plot, 
      path = plot_path,
      width = width,
      height = height)
  plot(plot)
}
```

```{r df-import, include=FALSE}
# Importing data
# a <- read_csv(F("data/current/ManikinData_WetDry.csv"))

df_wetdry <- read_csv(F("data/current/ManikinData_WetDry.csv"), 
    col_types = cols(
      wig = col_factor(levels = c("Nude", 
        "LowCurv", "MidCurv", "HighCurv")), 
      radiation = col_factor(levels = c("off", 
            "on")),
      wet_dry = col_factor(levels = c("dry", 
            "wet")),
      trial = col_factor(levels = c("1", "2", "3"))))
```

# Preparing data

## Estimating dry heat loss at 30C and solar influx

### Solar influx

Here we calculate solar influx and the temperature corrected heat loss for each experiment. 

Solar influx (difference between heat loss with radiation on and off) is calculated as:

$$Solar\ influx \ (W/m^2) = heatflux_{(radiation)}- heatflux_{(no \ radiation)}$$

```{r df-solar-influx}

df_influx <- df_wetdry %>% 
  pivot_longer(cols = c("heatloss", "resistance", "clo")) %>% 
  filter(name == "heatloss") %>% 
  select(-c(skin_temp, amb_temp, amb_rh)) %>% 
  pivot_wider(names_from = radiation, values_from = value) %>% 
  mutate(influx = off-on) %>% 
  drop_na() %>% 
  select(-name)

```

Here we plot the solar influx.

```{r plt-solar-influx}

df_influx %>% 
  ggplot(
    aes(x = wig,
        y = influx,
        fill = trial)) + 
  geom_col(position = position_dodge(width = 0.5)) +
  # ylim(0,200)+
  coord_flip() +
  theme_bw() +
  facet_grid(rows = vars(df_influx$wind), cols = vars(df_influx$wet_dry)) +
  labs(x = "Wig used on manikin", y = "Solar Influx in W/m2") +
  theme(plot.title = element_text(hjust = 0.5),
        axis.title.y = element_blank()) +
  scale_fill_brewer(type = "qual", palette = 'Dark2',  name = "Trial" )

```

A plot of solar influx shows an outlier in the wet experiments where the heat loss with solar radiation was somehow less than the heat loss without solar radiation. We will exclude this outlier.

```{r include=FALSE}

df_influx <- df_influx %>% 
  mutate(influx = replace(influx, influx<0, NA)) %>% 
  drop_na() %>% 
  distinct()

```


### Temperature correction (to 30 C)

For the dry heat loss experiments (measuring dry heat resistance), we had to run some experiments at different temperatures to create a large enough gradient between skin/surface temperature and ambient temperature. The manikin is only able to produce results by measuring heat loss, and at 0.3 m/s wind speed, we found that the straight hair and nude (no hair) conditions led to overheating of the manikin. Subsequently, we had to adjust the temperatures to create a temperature gradient. 

We thus need to bring all the measurements of heat loss to the same temperature. As heat resistance is temperature independent, we can use this to calculate the expected heat loss at various temperatures. We estimate heat loss at 30C with the following calculation. 

$$Heat\ loss (W/m^2)_{(30C\ no\ radiation)} = 5/heat\ resistance_{(no \ radiation)} $$
```{r df-30c-radoff, include=FALSE}

df_dry_off <- df_wetdry %>% 
  filter(radiation=="off" & wet_dry == "dry") %>% 
  select(c(wig, wind, wet_dry, resistance, trial)) %>% 
  distinct()

df_dry_off

df_dry30_off<- df_influx %>% 
  filter(wet_dry == "dry") %>% 
  left_join(., 
            df_dry_off) %>% 
  mutate(heatloss30 = 5/resistance) %>% 
  select(-c(on, off)) %>% 
  rename(off = heatloss30) %>% 
  distinct()

df_dry30_off

```



To calculate the heat loss at 30C with radiation, we subtract the solar influx from the temperature corrected heat loss:

$$Heat\ loss (W/m^2)_{(30C\ with\ radiation)}  = Heat\ loss (W/m^2)_{(30C\ no\ radiation)}- solar\ influx(W/m^2) $$

```{r df-30c-radon, include=FALSE}

df_dry_on <- df_wetdry %>% 
  filter(radiation=="on" & wet_dry =="dry") %>% 
  select(c(wig, wind, wet_dry, resistance, trial)) %>% 
  distinct()

df_dry_on

df_dry30<- df_dry30_off %>% 
  mutate(on = off-influx) %>% 
  select(-resistance) %>% 
  distinct()

df_dry30
```


```{r df-wet-dry, include=FALSE}

df_wetdry_final <- bind_rows(df_dry30, df_influx[df_influx$wet_dry == "wet",]) %>% 
  distinct()

df_wetdry_final

df_long_wetdry_final <- df_wetdry_final %>% 
  pivot_longer(influx:on, names_to = "var", values_to = "heatloss") %>% 
  distinct()

df_long_wetdry_final

```


# Exploratory plots

```{r df-summary, include=FALSE}
# means and sd
sum_manikin_df <- df_long_wetdry_final %>% 
  group_by(wig, wind, wet_dry, var)%>%
  summarise(mean = mean(heatloss), sd = sd(heatloss, na.rm = TRUE), 
            n= n()
  )

sum_manikin_df

```

```{r plt-solar-influx-error, fig.height=4, fig.width=7, include=FALSE}

plt_influx_line <- sum_manikin_df %>% 
    filter(var == "influx") %>% 
  ggplot( aes(x = wind, y = mean, group = wig, color = wig)) + 
    geom_line() +
    geom_point() +
    geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width = 0.2, position=position_dodge(0.05)) +
  facet_grid(cols = vars(wet_dry))+
  theme_classic()
  

pltsave_func(plt_influx_line, plot_path, width = 7, height = 4)

```

```{r plt-influx-dry, eval=FALSE, include=FALSE}

plt_influx_dry <- sum_manikin_df %>% 
    filter(var == "influx" & wet_dry == "dry") %>% 
  ggplot( aes(x = wind, y = mean, group = wig, color = wig)) + 
    geom_line() +
    geom_point() +
    geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width = 0.2, position=position_dodge(0.05)) +
  theme_classic()


```

```{r plt-influx-wet, include=FALSE}

plt_influx_wet <- sum_manikin_df %>% 
    filter(var == "influx" & wet_dry == "wet") %>% 
  ggplot( aes(x = wind, y = mean, group = wig, color = wig)) + 
    geom_line() +
    geom_point() +
    geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width = 0.2, position=position_dodge(0.05)) +
  theme_classic()


```


```{r plt-heatloss-influx-error, fig.height=4, fig.width=7, include=FALSE}

heatloss_sum_manikin_df <- sum_manikin_df %>% 
  filter(var != "influx") 

plt_heatloss_line <- ggplot(
  heatloss_sum_manikin_df, aes(x = wind, y = mean, group = wig, color = wig)) + 
    geom_line() +
    geom_point() +
    geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width = 0.2, position=position_dodge(0.05)) +
  facet_grid(cols = vars(var), rows = vars(wet_dry)) +
  theme_classic()
  

pltsave_func(plt_heatloss_line, plot_path, width = 7, height = 4)

```

```{r plt-heatloss-error-dry, eval=FALSE, fig.height=4, fig.width=7, include=FALSE}

plt_heatloss_line_off <- heatloss_sum_manikin_df %>%
    filter(var == "off" & wet_dry == "dry") %>% 
  ggplot( aes(x = wind, y = mean, group = wig, color = wig)) + 
    geom_line() +
    geom_point() +
    geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width = 0.2, position=position_dodge(0.05)) +
  theme_classic()
  
plt_heatloss_line_on <- heatloss_sum_manikin_df %>%
    filter(var == "on" & wet_dry == "dry") %>% 
  ggplot( aes(x = wind, y = mean, group = wig, color = wig)) + 
    geom_line() +
    geom_point() +
    geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width = 0.2, position=position_dodge(0.05)) +
  theme_classic()


```

```{r plt-heatloss-error-wet, eval=FALSE, fig.height=4, fig.width=7, include=FALSE}

plt_heatloss_line_off <- heatloss_sum_manikin_df %>%
    filter(var == "off" & wet_dry == "wet") %>% 
  ggplot( aes(x = wind, y = mean, group = wig, color = wig)) + 
    geom_line() +
    geom_point() +
    geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width = 0.2, position=position_dodge(0.05)) +
  theme_classic()
  
plt_heatloss_line_on <- heatloss_sum_manikin_df %>%
    filter(var == "on" & wet_dry == "wet") %>% 
  ggplot( aes(x = wind, y = mean, group = wig, color = wig)) + 
    geom_line() +
    geom_point() +
    geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width = 0.2, position=position_dodge(0.05)) +
  theme_classic()


```

```{r plt-dry, include=FALSE}

plt_dry_combo <- sum_manikin_df %>% 
    filter(wet_dry == "dry") %>% 
  mutate(var = factor(var, levels = c("off", "on", "influx"))) %>% 
  ggplot( aes(x = wind, y = mean, group = wig, color = wig)) + 
    geom_line() +
    geom_point() +
    geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width = 0.2, position=position_dodge(0.05)) +
  facet_grid(cols = vars(var))+
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(x = bquote('Wind speed'~(m/s)), y=bquote('Heat flux'~(W/m^2))) +
  theme_classic()

# pltsave_func(plt_dry_combo, plot_path, width = 8, height = 3)
  
  
  
```


```{r plt-wet, include=FALSE}

plt_wet_combo <- sum_manikin_df %>% 
    filter(wet_dry == "wet") %>% 
  mutate(var = factor(var, levels = c("off", "on", "influx"))) %>% 
  ggplot( aes(x = wind, y = mean, group = wig, color = wig)) + 
    geom_line() +
    geom_point() +
    geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width = 0.2, position=position_dodge(0.05)) +
  facet_grid(cols = vars(var))+
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(x = bquote('Wind speed'~(m/s)), y=bquote('Evaporative resistance'~(W/m^2))) +
  theme_classic()

# pltsave_func(plt_dry_combo, plot_path, width = 8, height = 3)
  
  
```

```{r plt-wetdry}

p1 <- plt_dry_combo / plt_wet_combo

p1 + plot_annotation(tag_levels = "A") + plot_layout(guides='collect')

```

## Sweating

We use the dry and wet data to infer the amount of sweat that a scalp could evaporate under conditions of solar radiation at 30C (maximum sweat capacity) and how much evaporative cooling from sweat would be needed to cancel out any heat gain (zero heat gain sweat). 


```{r df-sweat}

df_sweat <- sum_manikin_df %>% 
  select(-c(sd, n)) %>% 
  pivot_wider(names_from = c(wet_dry, var), values_from = mean) %>% 
  mutate(wet_dry_w_m2 = dry_off + wet_on,
         solar_w_m2 = dry_off - dry_influx,
         diff_dry_wet = wet_dry_w_m2 - solar_w_m2,
         sweat_max = diff_dry_wet/2430*3600,
         sweat_zero_gain = case_when(
           solar_w_m2 < 0 ~ abs(solar_w_m2/2430*3600),
           TRUE ~ 0
         )) %>% 
  # select(wig, wind, wet_dry_w_m2, solar_w_m2, diff_dry_wet, sweat_max, sweat_zero_gain)
  select(wig, wind, sweat_max, sweat_zero_gain) %>% 
  pivot_longer(sweat_max:sweat_zero_gain, names_to = "sweat_type", values_to = "mean")

```


Here, we plot the sweat rate potential (left) and the sweat rate required to cancel out heat gain at $T_{ambient} = 30^\circ C$.

```{r plt-sweat, fig.cap="The quantity of sweat that can be maximally evaporated (left) and that is required for zero heat gain (right) with various head coverings under three wind speeds", fig.height=3, fig.width=6}
plt_sweat_max_zero <- ggplot(df_sweat, aes(wind, mean)) +
  geom_point(aes(color=wig, fill=wig)) +
  geom_path(aes(group=wig, color=wig))+
  theme_classic() +
  labs(x = bquote('Wind speed'~(m/s)),
       y=bquote('Sweat'~(g/m^2/h))) +
  facet_wrap(vars(sweat_type))

pltsave_func(plt_sweat_max_zero, plot_path, width = 8, height = 4)
```

What emerges is that while heat loss potential is higher without hair as a barrier (i.e. the "nude" condition), the *potential* sweat far exceeds the physiologically possible sweat rate for humans. The plot for zero heat gain shoes that a nude scalp requires the most sweat and this requirement is inversely correlated with hair curvature.

```{r plt-combo, eval=FALSE, include=FALSE}

# p1 <- plt_dry_combo / plt_wet_combo
# 
# plt_dry_combo <- plt_dry_combo +
#   theme(legend.position = "none")
# 
# plt_wet_combo <- plt_wet_combo +
#   theme(legend.position = "none")

plt_dry_combo + 
  plt_wet_combo + plot_layout(ncol = 1) +
  (plt_sweat_max_zero + guide_area() + plot_layout(widths = c(2,1), guides = "collect")) + plot_annotation(tag_levels = "A")

# plt_dry_combo + plt_wet_combo + (plt_sweat_max_zero + guide_area()) + plot_layout(ncol = 1, guides = "collect", a) 

# plot_annotation(tag_levels = "A") + plot_layout(guides='collect')

```

# Regression models

## Dry heat loss


### Radiation off

Here, we model the effect of the `wig` variable on the `off` (heat loss without radiation) variable while correcting for `wind`. 

Without radiation, having hair will reduce the heat loss.

```{r lm-dry-heatloss-off}

# df <- df_wetdry_final %>% 
#   filter(wet_dry == "dry")

df_dry_off <- df_wetdry_final %>%
  filter(wet_dry == "dry")

# df_dry_off
model_dry_off<- lm(off~wind+wig, data=df_dry_off)
summary(model_dry_off)

```


### Radiation on

With radiation, there is a net increase in heat (i.e. heat gain) without any hair. Additonally, we observe that heat gain decreases with increasingly curled hair.

```{r lm-dry-heatloss-on}
# 
# df <- df_wetdry_final %>% 
#   filter(wet_dry == "dry")
df_dry_on <- df_wetdry_final %>% 
  filter(wet_dry == "dry")

model_dry_on<- lm(on~wind+wig, data=df_dry_on)
summary(model_dry_on)



# summ(model_dry_on, scale = TRUE, confint = TRUE, digits = 5)
# 
# plot_summs(model_dry_on, scale = TRUE, inner_ci_level = .9)
```

### Solar influx

Here, we model the effect of the `wig` variable on `influx` while correcting for `wind`. 

In the dry heat loss experiments, we see that all hair (regardless of curliness) decreases the solar influx. Additionally, the curlier the hair, the lower the solar influx.


```{r lm-dry-influx}
df_dry <- df_wetdry_final %>% 
  filter(wet_dry == "dry")


model_dry <- lm(influx~wind+wig, data=df_dry)

summary(model_dry)
```


### Summary of all dry heat loss models

```{r eval=FALSE, include=FALSE, results='asis'}

export_summs(model_dry_off, model_dry_on, model_dry, scale = TRUE, error_format = "[{conf.low}, {conf.high}]")
```

```{r plt-summary-models, eval=FALSE, include=FALSE}

plot_summs(model_dry_off, model_dry_on, model_dry, scale = TRUE,  model.names = c("Radiation Off", "Radiation On", "Solar Influx"))

```



## Evaporative resistance (wet experiments)

Here, we repeat the same modelling process for the evaporative resistance data from the wet experiments.


### Radiation off

Here, we model the effect of the `wig` variable on the `off` (heat loss without radiation) variable while correcting for `wind`. 

Without solar radiation, all hair (regardless of texture) decreases evaporative resistance. 

```{r lm-wet-heatloss-off}

df <- df_wetdry_final %>% 
  filter(wet_dry == "wet")
df_wet_off <- df_wetdry_final %>% 
  filter(wet_dry == "wet")
model_wet_off<- lm(off~wind+wig, data=df_wet_off)
summary(model_wet_off)
```

### Radiation on

With radiation, hair decreases evaporative resistance. 

```{r lm-wet-heatloss-on}

df <- df_wetdry_final %>% 
  filter(wet_dry == "wet")
df_wet_on <- df_wetdry_final %>% 
  filter(wet_dry == "wet")
model_wet_on<- lm(on~wind+wig, data=df_wet_on)
summary(model_wet_on)
```


### Solar influx

Combining the above data to calculate solar influx, we see that there is not a considerable effect of radiation on evaporative resistance.

```{r lm-wet-influx}

df <- df_wetdry_final %>% 
  filter(wet_dry == "wet")

df_wet <- df_wetdry_final %>% 
  filter(wet_dry == "wet")

model_wet <- lm(influx~wind+wig, data=df_wet)

model_wet

plot(model_wet)
summary(model_wet)
```


